Do we need detailed demographic data to forecast the impacts of climate change on plant populations?

### 2015-07-25 esa_talk/esa2015.Rmd
updates figure 2 MAE

ggplot(subset(plotd, variable!="mean_cover"), aes(x=species, y=value, fill=model))+
  geom_bar(stat="identity", position="dodge")+
  facet_wrap("variable", nrow=1, scales="free")+
  scale_fill_manual(values = c("darkorange", "steelblue"))
```

>>>>

ggplot(subset(plotd, variable!="mean_cover"), aes(x=species, y=value, fill=model))+
  geom_bar(stat="identity", position="dodge", color="white")+
  facet_wrap("variable", nrow=1, scales="free")+
  scale_fill_manual(values = c("darkorange", "steelblue"))+
  theme_bw()
```
